IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-12 main.tex
:triangular_flag_on_post: arXiv and TCOM 120821

		To evaluate the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links. $d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference. The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively. We consider a large open space Wi-Fi-like environment at center frequency \SI{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{Erceg2004}. Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \SI{10}{\meter}, and \num{3.5} onwards to further penalize the channels with large distance. All fadings are modeled as Non-LoS (NLoS) with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d. CSCG variables. Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$. We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (and one-dimensional search to obtain the R-E region). Each R-E point is averaged over \num{100} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.

		\begin{figure}[!t]
			\centering
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/channel_amplitude.tex}
			}
			\caption{Sorted equivalent subchannel amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
			\label{fi:channel_amplitude}
		\end{figure}

@@

		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}. First, adding either active or passive elements enhances the equivalent channel strength and boosts both information and power transfer, but has negligible influence on the optimal receiving strategy. Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design. To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}. As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dBA} gap compared to the nonlinear model-based SMF and GP designs. Third, passive beamforming has a larger array gain and power scaling order than active beamforming. This behavior is more obvious in the case of WIT and WPT. For active beamforming, doubling $M$ brings a \SI{3}{\dBA} gain at the output SNR, which corresponds to a transmit array gain of $M$ \cite{Tse2005} and a doubled harvester input power. Thanks to the rectenna nonlinearity, the output DC ends up with a nearly four-time (\SI{12}{\dBA}) increase, which aligns with the active scaling law in the order of $M^2$ \cite{Clerckx2018b}. On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dBA}, which implies a reflect array gain of $L^2$ \cite{Wu2019}. An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$. Hence, doubling the number of IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC by \num{16} times (\SI{24}{\dBA}), corresponding to a passive scaling law in the order of $L^4$. Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link. These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the waveform and beamforming design.

>>>>

		To evaluate the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links. $d_{\mathrm{D}}=\SI{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$ are chosen as reference. The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively. We consider a large open space Wi-Fi-like environment at center frequency \SI{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{Erceg2004}. Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \SI{10}{\meter}, and \num{3.5} onwards to further penalize the channels with large distance. All fadings are modeled as Non-LoS (NLoS) with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d. CSCG variables. Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ \cite{Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$. We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\SI{40}{\dBm}$, the receive antenna gain as \SI{3}{\dBi}, the scaling ratio as $\alpha=2$, the tolerance as $\epsilon=10^{-8}$, and assume $\delta=\rho$ for simplicity (and one-dimensional search to obtain the R-E region). Each R-E point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.

		\begin{figure}[!t]
			\centering
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/channel_amplitude.tex}
			}
			\caption{Sorted equivalent subchannel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
			\label{fi:channel_amplitude}
		\end{figure}

@@

		The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}. First, it is observed that adding either active or passive elements can improve the equivalent SNR and produce a nearly concave R-E region, which suggests that the receiver should operate in the PS mode in such cases. Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design. To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that 1) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; 2) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}. As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \SI{20}{\dBA} gap compared to the nonlinear model-based SMF and GP designs. Third, passive beamforming has a larger array gain and power scaling order than active beamforming. This behavior is more obvious in the case of WIT and WPT. For active beamforming, doubling $M$ brings a \SI{3}{\dBA} gain at the output SNR, which corresponds to a transmit array gain of $M$ \cite{Tse2005} and a doubled harvester input power. Thanks to the rectenna nonlinearity, the output DC ends up with a nearly four-time (\SI{12}{\dBA}) increase, which aligns with the active scaling law in the order of $M^2$ \cite{Clerckx2018b}. On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dBA}, which implies a reflect array gain of $L^2$ \cite{Wu2019}. An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$. Hence, doubling the number of IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC by \num{16} times (\SI{24}{\dBA}), corresponding to a passive scaling law in the order of $L^4$. Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link. These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the waveform and beamforming design.
